---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# bhappyr

R package: Amusing Sentences Generator. Includes addin.

Generates amusing feedback to lighten the mood of statisticians. Contains addin as well as sentence generator functions.

Pass new structures and word lists to generate unique sentences.  

By Ludvig R. Olsen,  
Cognitive Science, Aarhus University.  
Started in March, 2017 

Contact at:
r-pkgs@ludvigolsen.dk

Main functions:   

* generateHappyFeedback (Also addin)
* generate_sentence

## Installation  

>
> install.packages("devtools")   
>
> devtools::install_github("LudvigOlsen/bhappyr")  
>

## Use addin

* Install package.
* Add key command by going to:   
    - *Tools* > *Addins* > *Browse Addins* > *Keyboard Shortcuts*.  
    - Find **Become Happy** and press its field under *Shortcut*. 
    - Press desired key command.
    - Press *Apply*.
    - Press *Execute*.
* Press chosen key command inside RStudio.

## Examples

### Addin: generateHappyFeedback()

Quickly generate a (hopefully) amusing sentence.

```{r}
# Attach package
library(bhappyr)

generateHappyFeedback()
generateHappyFeedback()
generateHappyFeedback()
```

### Generate sentences with more control

Pass new structures and word lists and turn off internal structures and word lists.

```{r}
# Attach package
library(bhappyr)

# Create structures
st <- c("[salutation]! You are [positive_adj] today! ;)",
        "You [positive_vb_past] that code! [positive_adj]!")

# Create list of word lists
wl <- list("salutation" = c("Sir", "Mother", "Dear", "Friend"),
           "positive_adj" = c("beautiful", "bright", "smart"),
           "positive_vb_past" = c("accomplished","played", "modified"))

## Example 1
# Using internal structures + word lists

# Generate 1 sentence
generate_sentence()

## Example 2
# Providing structures
# and not using internal structures

# Generate 2 sentences
generate_sentence(n = 2, structures = st,
                  int_structures = FALSE)

## Example 3
# Providing word_lists and structures
# and not using internal word_lists and structures

# Generate 3 sentences
generate_sentence(n = 3, structures = st,
                  word_lists = wl,
                  int_structures = FALSE,
                  int_word_lists = FALSE)

```


